Market Simulator

### 2020-08-19 analysis/05_market_simulator.Rmd
updates

p1_politic_pref <- reactive({
  input$p1_political_pref
})

@@

    # beta_persona$p1_value[beta_persona$levels %in% input == '0'] <- 0
    # beta_persona$p1_value[beta_persona$levels %in% input == '1'] <- 1
    # beta_persona$p1_value[beta_persona$levels %in% input == '2'] <- 2
    # beta_persona$p1_value[beta_persona$levels %in% input == '3'] <- 3
    # beta_persona$p1_value[beta_persona$levels %in% input == '4'] <- 4
    # beta_persona$p1_value[beta_persona$levels %in% input == '5'] <- 5
    # beta_persona$p1_value[beta_persona$levels %in% input == '6'] <- 6
    # beta_persona$p1_value[beta_persona$levels %in% input == '7'] <- 7

@@

    beta_persona$p1_value[beta_persona$levels == "Political Preference"] <- p1_politic_pref()

@@

@@

sliderInput("p1_political_pref",
       label = "Political Preference",
       min = 0,
       max = 7,
       value = 0)

selectInput("p1_national_news",
         label = "Follow national news:",
         choices = c('Multiple times a day' = "1",
                     'Every day' = "2",
                     "Once a week" = "3",
                     "Hardly ever" = "4",
                     "Never" = "5"),
         width = "200px")

@@

>>>>

p1_politic_pref <- reactive({
  max(input$p1_political_pref)
})

@@

    beta_persona$p1_value[beta_persona$levels %in% input$p1_political_pref] <- 1
    # beta_persona$p1_value[beta_persona$levels %in% input == '1'] <- 1
    # beta_persona$p1_value[beta_persona$levels %in% input == '2'] <- 2
    # beta_persona$p1_value[beta_persona$levels %in% input == '3'] <- 3
    # beta_persona$p1_value[beta_persona$levels %in% input == '4'] <- 4
    # beta_persona$p1_value[beta_persona$levels %in% input == '5'] <- 5
    # beta_persona$p1_value[beta_persona$levels %in% input == '6'] <- 6
    # beta_persona$p1_value[beta_persona$levels %in% input == '7'] <- 7

@@

    # beta_persona$p1_value[beta_persona$levels == "Political Preference"] <- 1

@@

  df[,2] <- c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")
  df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
  df[,4] <- c(rep("Persona 1",8), rep("Persona 2", 8), rep("Persona 3", 8))

  colnames(df) <- c('Value', 'Organization', "Type", "Persona")

@@

# sliderInput("p1_political_pref",
#        label = "Political Preference",
#        min = 0,
#        max = 7,
#        value = 0)

selectInput("p1_national_news",
         label = "Follow national news:",
         choices = c('Multiple times a day' = 1,
                     'Every day' = 2,
                     "Once a week" = 3,
                     "Hardly ever" = 4,
                     "Never" = 5))

@@

# selectInput("p1_political_pref",
#          label = "Political views from liberal to conservative:",
#          choices = c("0", '1', '2', '3','4','5','6','7'))
